---
title: "315 Project Draft"
author: "Minami Makino"
date: "11/11/2018"
output: 
  html_document:
    toc:  true
    toc_float:  true
    code_folding:  hide
---

```{r}
library(tidyverse)
countries <- read.csv("countriesoftheworld2.csv")
countries$Climate <- factor(countries$Climate)
countries$X <- NULL
colnames(countries) <- c("Country", "Region", "Population", "Area", 
                         "Pop_Density", "Coastline", "Net_Migration",
                         "Infant_Mortality", "GDP_per_cap", "Literacy_Rate",
                         "Phones", "Arable", "Crops", "Other", "Climate",
                         "Birthrate", "Deathrate", "Agriculture", "Industry",
                         "Service")

cbbPalette = c("royalblue", 'dodgerblue','grey',"aquamarine4", "orange", 'indianred', "darkviolet", "darkgreen", "goldenrod3", "burlywood4", "deeppink4")


shreyap_315_theme <-  theme_bw() + 
  theme(axis.text = element_text(color = "darkslategrey"),
        text = element_text(color = "dark blue", size = 30), legend.key.size = unit(5, "lines"))
```


We are first looking at the continuous variables of literacy, GDP, birthrate, deathrate, agriculture, industry, and service of the countries of the world dataset. From this dendrogram, we can see that these continuous variables do a pretty good job of clusifing the Western European and African regions which correspond to the highest and lowest GDPs respectively.

```{r, warning = F, message = F}
library(dendextend)
pdf("/Users/shreyaprakash/Documents/36315/Graphics_Project/Dendro3.pdf", width=20, height=30,onefile=T)
countries_cont <- dplyr::select(countries, GDP_per_cap, Literacy_Rate, 
                           Birthrate, Deathrate, Agriculture,
                           Industry, Service)

dend <- countries_cont %>% scale %>% dist %>% hclust %>% as.dendrogram

get_colors <- function(x, palette = cbbPalette) palette[match(x, unique(x))]


dendro_plot <- dend %>% set("labels", trimws(countries$Region), order_value = TRUE) %>% 
  set("labels_col", get_colors(countries$Region), order_value = TRUE) %>% set("labels_cex", .6) %>%
  ggplot(horiz = T) + 
  labs(
    title = "Cluster Dendogram of Countries Regions",
    y = "Pairwise Euclidean Distance",
    x = ""
  ) + 
  theme(axis.text = element_text(color = "darkslategrey"),
        text = element_text(color = "dark blue", size = 40), legend.key.size = unit(5, "lines"))

print(dendro_plot)
```


```{r}
pdf("/Users/shreyaprakash/Documents/36315/Graphics_Project/Density.pdf", width=20, height=12,onefile=T)
countries <- mutate(countries, 
                                 Region = factor(Region))

countries_cont_scale <- scale(countries_cont)

dist_countries_cont <- dist(countries_cont_scale)

countries_new <- cmdscale(dist_countries_cont)

countries_new <- data.frame(countries_new)

colnames(countries_new) <- c("coordinate_1", "coordinate_2")

countries_new <- countries_new %>% mutate(Region = countries$Region)



density <- ggplot(data = countries_new, 
       aes(x = coordinate_1, y = coordinate_2)) +
  geom_density2d(h = c(1.25, 3)) +
  geom_point(aes(color = Region),
             size = 5, alpha = 0.8) +
  xlim(-4, 6) + 
  ylim(-3.5, 5.2) +
  labs(x = "MDS Coordinate 1", 
       y = "MDS Coordinate 2", 
       color = "Region",
       title = "Compression of Countries of the World") + 
  shreyap_315_theme + scale_color_brewer(palette="Spectral")

print(density)
```

Can see that there is clustering for regions again when across Population, Literacy rate, and GDP.
