---
title: "315_graphs"
author: "Shreya Prakash"
date: "November 9, 2018"
output: html_document
---

```{r, message=FALSE, warning=FALSE}
library(tidyverse)

cbbPalette <- c("#000000", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")

shreyap_315_theme <-  theme_bw() + 
  theme(axis.text = element_text(color = "darkslategrey"),
        text = element_text(color = "dark blue", size = 30), legend.key.size = unit(5, "lines"))
```


```{r, message=FALSE, warning=FALSE}
countries <- read.csv("countriesoftheworld2.csv")
countries$Climate <- factor(countries$Climate)
countries$X <- NULL
colnames(countries) <- c("Country", "Region", "Population", "Area", 
                         "Pop_Density", "Coastline", "Net_Migration",
                         "Infant_Mortality", "GDP_per_cap", "Literacy_Rate",
                         "Phones", "Arable", "Crops", "Other", "Climate",
                         "Birthrate", "Deathrate", "Agriculture", "Industry",
                         "Service")
```


```{r, message=FALSE, warning=FALSE}
pdf("/Users/shreyaprakash/Documents/36315/Graphics_Project/hist.pdf", width=20, height=16,onefile=T)

cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7", "#000000", "")

hist_gdp <- ggplot(countries, aes(x = GDP_per_cap, fill = Region)) + 
  geom_histogram(alpha = 0.7, bins = 15, col = "black") + 
  labs(
    title = "Distribution of GDP per Capita",
    x = "GDP per Capita",
    y = "Frequency of GDP per Capita",
    fill = "Region"
  ) + shreyap_315_theme + scale_fill_brewer(palette="Spectral")

print(hist_gdp)
```

+ The Distribution of GDP per Capita is skewed right
+ Regions like Sub-Saharan Africa and Oceania have lower GDP per Capita compared to regions like North America and Western Europe

```{r, message=FALSE, warning=FALSE}
pdf("/Users/shreyaprakash/Documents/36315/Graphics_Project/birth.pdf", width=20, height=16,onefile=T)

birth <- ggplot(countries, aes(y = log(GDP_per_cap), x = Birthrate)) + 
  geom_point(aes(color = Region), size = 5) + 
  geom_smooth(method = lm, se = FALSE) + 
  labs(
    title = "Log of GDP per Capita vs Birthrate",
    x = "Birthrate",
    y = "Log of GDP per Capita"
  ) + shreyap_315_theme + scale_color_brewer(palette="Spectral")

print(birth)
```

+ Birth rate is negatively linearly related to log of the GDP per Capita. 
+ Regions like Sub-Saharan Africa have high birth rate and low log GDP per Capita
+ Regions like Western Europe have low birth rate and high log GDP per capita.
