---
title: "masaherm_graphs"
author: "Masahero Masuda"
date: "11/12/2018"
output: html_document
---

```{r, message=FALSE, warning=FALSE}
library(ggplot2)
library(MASS)
cbbPalette <- c("#000000", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")

shreyap_315_theme <-  theme_bw() + 
  theme(axis.text = element_text(color = "darkslategrey"),
        text = element_text(color = "dark blue"))
```

```{r, message=FALSE, warning=FALSE}
library(dplyr)
library(reshape2)
library(gridExtra)

countries <- read.csv("countriesoftheworld2.csv")
agg.countries <- aggregate(countries, by = list(countries$Region), mean)
agg_countries_industries <- dplyr::select(agg.countries, Agriculture, 
                                          Industry, Service, Group.1)

dat.m <- melt(agg_countries_industries, id.vars = "Group.1")

ggplot(dat.m, aes(x = Group.1, y = value, fill=variable)) +
    geom_bar(stat='identity') + 
  shreyap_315_theme +
    theme(axis.text.x = element_text(angle = 55, hjust = 0.75, vjust = .9, size = 6, ), legend.text.align = 0) +
    labs(
         title = "Proportion of Industy for each Region", 
         x = "Region",
         y = "Proportion of Industry", 
         fill = "Industry"
         )

```

It is apparent from the graph that Sub-Saharan Africa has the highest percentages of those working in agriculture. On the other hand Near East and Northern American regions have the highest percentages of Industry-related jobs, which is sensible since these regions are more developed compared to others. Finally Northern America and Western Europe have the highest percentages of service-related jobs compared to other regions, which again is related to their development as a nation.


```{r, warning = FALSE, message = FALSE}
library(ggmap)
library(rworldmap)
library(maptools)
library(maps)

#mp <- NULL
#mapWorld <- borders("world", colour="gray50", fill="gray50")
#mp <- ggplot() + mapWorld
#mp <- joinCountryData2Map(countries, joinCode="NAME", nameJoinColumn="Country")

spdf <- joinCountryData2Map(countries, joinCode="NAME", nameJoinColumn="Country")

mapCountryData(spdf, nameColumnToPlot="Phones..per.1000.", catMethod="fixedWidth", colourPalette = "diverging", mapTitle = "Number of Phones per 1000") 
```

