---
title: "masaherm_graphs"
author: "Masahero Masuda"
date: "11/12/2018"
output: html_document
---

```{r, message=FALSE, warning=FALSE}
library(ggplot2)
library(MASS)
cbbPalette <- c("#000000", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")

shreyap_315_theme <-  theme_bw() + 
  theme(axis.text = element_text(color = "darkslategrey"),
        text = element_text(color = "dark blue"))
```

```{r, message=FALSE, warning=FALSE}
library(dplyr)
library(reshape2)
library(gridExtra)
countries <- read.csv("countriesoftheworld2.csv")
agg.countries <- aggregate(countries, by = list(countries$Region), mean)


agriculture <- ggplot(agg.countries) +
    geom_bar(aes(x = Group.1,y = Agriculture),stat = "identity", 
             fill = "green") +
    shreyap_315_theme + 
    theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 1)) +
    labs(title = "Agriculture", x = "Region")

industry <- ggplot(agg.countries) +
    geom_bar(aes(x = Group.1, y = Industry), stat ="identity",
             fill = "blue") +
    shreyap_315_theme +
    theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 1)) +
    labs(title = "Industry", x = "Region")

service <- ggplot(agg.countries) +
    geom_bar(aes(x = Group.1, y = Service), stat ="identity",
             fill = "red") +
    shreyap_315_theme +
    theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 1)) +
    labs(title = "Service", x = "Region")

grid.arrange(agriculture, industry, service, ncol = 3)
```

It is apparent from the graph that Sub-Saharan Africa has the highest percentages of those working in agriculture. On the other hand Near East and Northern American regions have the highest percentages of Industry-related jobs, which is sensible since these regions are more developed compared to others. Finally Northern America and Western Europe have the highest percentages of service-related jobs compared to other regions, which again is related to their development as a nation.


```{r, warning = FALSE, message = FALSE}
library(ggmap)
library(rworldmap)
library(maptools)
library(maps)

#mp <- NULL
#mapWorld <- borders("world", colour="gray50", fill="gray50")
#mp <- ggplot() + mapWorld
#mp <- joinCountryData2Map(countries, joinCode="NAME", nameJoinColumn="Country")

spdf <- joinCountryData2Map(countries, joinCode="NAME", nameJoinColumn="Country")

mapCountryData(spdf, nameColumnToPlot="Phones..per.1000.", catMethod="fixedWidth", colourPalette = "diverging", mapTitle = "Number of Phones per 1000") 
```

