---
title: "wanhez_graphs"
author: "Wanhe Zhao"
date: "11/12/2018"
output: html_document
---

```{r, message=FALSE, warning=FALSE}
library(ggplot2)
library(MASS)
cbbPalette <- c("#000000", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")

shreyap_315_theme <-  theme_bw() + 
  theme(axis.text = element_text(color = "darkslategrey"),
        text = element_text(color = "dark blue"))
```

```{r, message=FALSE, warning=FALSE}
countries <- read.csv("countriesoftheworld2.csv")
countries$Climate <- factor(countries$Climate)
countries$X <- NULL
colnames(countries) <- c("Country", "Region", "Population", "Area", 
                         "Pop_Density", "Coastline", "Net_Migration",
                         "Infant_Mortality", "GDP_per_cap", "Literacy_Rate",
                         "Phones", "Arable", "Crops", "Other", "Climate",
                         "Birthrate", "Deathrate", "Agriculture", "Industry",
                         "Service")
```

```{r}
as.character(countries$Region[2])
```


```{r, message=FALSE, warning=FALSE}
ggplot(countries, aes(y = log(GDP_per_cap), x = Literacy_Rate)) + 
  geom_point(aes(color = Region)) + 
  geom_smooth(method = lm, se = FALSE) +
  labs(
    title = "Log of GDP per Capita vs Literacy Rate",
    x = "Literacy Rate",
    y = "Log of GDP per Capita"
  ) + shreyap_315_theme + scale_color_brewer(palette="Spectral")
```


+ There is a positive relatioship between literacy rate and log of the GDP per Capita. Approximately polynomial relationship.   
+ Literacy rate mostly depends on regions. Like sub-Saharan Africa, northern Africa and Latin America are lower litercy rate and GDP per capita. 
+ However, some regions show apparent high literacy rate like Western Europe, which has high literacy rate and high log GDP per capita.


```{r, warning = FALSE, message = FALSE}
pdf("/Users/wanhezhao/Box Sync/Fall2018/36315/project 1/Graphs/Literacy.pdf", width=12, height=8,onefile=T)

library(rworldmap)
countries2 <- read.csv("countriesoftheworld.csv", dec = ",")

countries2$X <- NULL
colnames(countries2) <- c("Country", "Region", "Population", "Area", 
                         "Pop_Density", "Coastline", "Net_Migration",
                         "Infant_Mortality", "GDP_per_cap", "Literacy_Rate",
                         "Phones", "Arable", "Crops", "Other", "Climate",
                         "Birthrate", "Deathrate", "Agriculture", "Industry",
                         "Service")
countries2 <- countries2[!is.na(countries2$Literacy_Rate),]
spdf <- joinCountryData2Map(countries2, joinCode="NAME", nameJoinColumn="Country")

plot3 <- mapCountryData(spdf, nameColumnToPlot="Literacy_Rate", catMethod="fixedWidth", colourPalette = c("royalblue", 'dodgerblue','grey',"yellow", "orange", 'indianred'), mapTitle = "Literacy Rate by Countries") 
print(plot3)

```

```{r}
library(rworldmap)
pdf("/Users/wanhezhao/Box Sync/Fall2018/36315/project 1/Graphs/service.pdf", width=12, height=8,onefile=T)

countries2 <- read.csv("countriesoftheworld.csv", dec = ",")

countries2$X <- NULL
colnames(countries2) <- c("Country", "Region", "Population", "Area", 
                         "Pop_Density", "Coastline", "Net_Migration",
                         "Infant_Mortality", "GDP_per_cap", "Literacy_Rate",
                         "Phones", "Arable", "Crops", "Other", "Climate",
                         "Birthrate", "Deathrate", "Agriculture", "Industry",
                         "Service")
countries2 <- countries2[!is.na(countries2$Service),]
spdf <- joinCountryData2Map(countries2, joinCode="NAME", nameJoinColumn="Country")

plot1 <- mapCountryData(spdf, nameColumnToPlot="Service", catMethod="fixedWidth", colourPalette = c("royalblue", 'dodgerblue','darkolivegreen1',"yellow", "orange", 'indianred'), mapTitle = "Service Sector and GDP per Capita by Countries") 

plot2 <- mapBubbles(spdf,nameZSize='GDP_per_cap',  nameZColour = adjustcolor("navy", alpha.f = 0.7),add = T, fill=TRUE, addColourLegend = F, addLegend = F, pch=21, symbolSize=.2,catMethod="fixedWidth")
print(plot1)
print(plot2)
```

```
plot2 <- mapBubbles(spdf,nameZSize='GDP_per_cap', nameZColour='navy', colourPalette = "red",add = T, 
     addColourLegend = F, addLegend = F, pch=21, symbolSize=.2,catMethod="fixedWidth",  alpha.f = 0.5)

print(plot1)
print(plot2)
```


+ Majority of the countries Literacy Rate are above 50 percentages
+ Countries in Africa shows relatively lower literacy rate
+ Litercy Rates are divergent between regions. 

